Homework

### 2016-07-04 Macro Impacts Revised.tex
update

Since we know that the total energy is, assuming that the velocity of the macro remains approximately constant throughout its journey through Earth

>>>>

Since we know that the total energy is (assuming that the velocity of the macro remains approximately constant throughout its journey through Earth) we can calculate the initial overpressure.
